\textbf{The Illusion Game: A Novel Experimental Paradigm Provides Evidence in Favour of a General Factor of Visual Illusion Sensitivity and Personality Correlates}

### 2022-09-07 manuscript.Rmd
Update manuscript.Rmd

Notably, the presence of a common mechanism underlying the effect of different illusions has been contested [@hamburger2016; @cretenoud2019a; @cretenoud2020]; and the nature of the underlying processes - whether related to low-level features of the visual processing system [@cretenoud2019; @gori2016] or to top-down influences of prior beliefs [@teufel2018; @caporuscio2022] are strongly debated. The existence of dispositional correlates of illusion sensitivity - for example, higher illusion resistance has been reported in schizophrenia and autism [@notredame2014; @park2022; @giaouri2011; @keane2014; @pessoa2008], as well as in individuals with stronger aggression and narcissism traits [@zhang2017; @konrath2009seeing] - is another area of controversy.

>>>>

Notably, the presence of a common mechanism underlying the effect of different illusions has been contested [@hamburger2016; @cretenoud2019a; @cretenoud2020]; and the nature of the underlying processes - whether related to low-level features of the visual processing system [@cretenoud2019; @gori2016] or to top-down influences of prior beliefs [@teufel2018; @caporuscio2022] are strongly debated. The existence of dispositional correlates of illusion sensitivity is another area of controversy, with some studies reporting higher illusion resistance in patients with schizophrenia and autism [@notredame2014; @park2022; @giaouri2011; @keane2014; @pessoa2008] and in individuals with stronger aggression and narcissism traits [@zhang2017; @konrath2009seeing].
